%-------------------------
% Resume in Latex
% Author : Pradeep Dantuluri
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://pradeep122.github.io}{\Large Pradeep Dantuluri}}  & Mobile : +91 897-817-3535 \\
  Email : \href{mailto:pradeep122@gmail.com}{pradeep122@gmail.com} & Skype : pradeep011 \\
\end{tabular*}


%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Expertise}{: Functional Programming, Micro Services, DevOps, Project Management, Team Building }
    }
    \item{
     \textbf{Technologies}{: Java8, Scala, RxJava, Play, Docker, Kubernetes, Promethues, Vault, Keycloak }
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Yantranet}{Hyderabad, India}
      {Co-Founder, Head of Engineering \& Product}{April 2012 - Present}
      \resumeItemListStart
        \resumeItem{YantraPlatform} 
          {A bespoke IoT platform designed for media intensive applications like Digital Signage and Kiosks. Allows for monitoring and pixel-level managmenent of thousands of screens spread across the world. \href{https://yantranet.com}{https://www.yantranet.com} }
        \resumeItem{YantraSign}
          {A Digital Signage solution that leverages the YantraPlatorm to deliver seamless control over content delivery, across a network of screens. \href{https://yantrasign.com}{https://yantrasign.com} }
        \resumeItem{ScreenVive} 
          {Content as a Service for your Digital Screens. Access a variety of configurable content feeds ranging from  news, entertainment, trivia etc to be used on your screens. \href{https://screenvive.com}{https://screenvive.com} }
        \item{Yantranet is a fully bootstrapped company, and have been cash-flow positive since day one. We are a part of \href{http://10000startups.com/our-startups}{NASSCOM 10K incubator} and \href{http://xlr8ap.com}{XLR8 AP accelerator}. We are based out of CT, USA with a Develoment Center in Hyderabad India.  }
        \item{Built the team from groud up to 20, by hiring teams for Web, Android , Backend, Design and QA }
        \item{I server as the Lead Architect for Web and Android Apps and Backend Services for YantraPlatform, YantraSign and ScreenVive}
        \item{Championed the migration to a Micro Serive Architecture and Kubernetes Deployments within the company}
        \item{I have Setup \& maintained the complete DevOps pipeline using Bitbucket, Jenkins, Docker, Kubernetes, Promethues}
      \resumeItemListEnd
  
    \resumeSubheading
      {DERI, NUI Galway}{Galway, Ireland}
      {Research Associate}{August 2008 - September 2011}
      \resumeItemListStart
        \resumeItem{Digi.me}
          {An EU funded research project to develop an Intelligent Trust-enhancing Store of a User’s personal information sphere in digital and social environments.}
        \resumeItem{Nepomuk}
          {A Social Semantic Desktop built on top of KDE which enables a deeper inter-connection of data from various applications using RDF other Semantic Web Tehcnologies }
        \resumeItem{Publications}
          {I co-authored 4 research papers and a journal in the field of  NLP and Semantic Web}
        \resumeItem{Skills Learnt}
          {Java, Python, GWT, RDF, OWL, Reseach, Academic Writing }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Side Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tickscore}{Hyderabad, India}
      {Technical Co-Founder}{January 2017 -- April 2019}
      \resumeItemListStart
        \item {An online service helping students prepare for the Civil Services Examination in India. Students could practise either online or using an Android App, against a well-curated set of questions and get detailed analytics on their progress. I designed and developed the backend services.}
        \resumeItem{Skills Learnt}
          {Javascript, NodeJS, ReactJS, ReactNative }
      \resumeItemListEnd
    \resumeSubheading
      {InMins}{Hyderabad, India}
      {Technical Co-Founder}{January 2011 -- April 2012}
      \resumeItemListStart
        \item{A food delivery app created long before mobile apps became prevelant. It was a web-based service, which catered to foodies in Hyderabad, India. I desinged and devloped the customer-facing web app and an administration console, for managing daily operations. }
        \resumeItem{Skills Learnt}
          {Java, Spring, Javascript, Bootstrap, Backbone, JQuery  }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Instutute of Information Technology}{Allahabad, India}
      {Bachelor of Technology in Information Technology;  GPA: 7.98/10.0 }{ 2004 -- 2008}
  \resumeSubHeadingListEnd



%--------PROGRAMMING SKILLS------------
% \section{Programming Skills}
%  \resumeSubHeadingListStart
%     \item{
%      \textbf{Languages}{: Scala, Java, Javascript, Python}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%     }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
